Review of Polymer Solutions for Near-Field Electrospinning with Spatial Control

### 2019-06-18 NFES_Review/article.tex
new intro

\begin{abstract}
Near-field electrospinning (NFES) have demonstrated to be one of the top techniques for the fabrication of nano and micro fibers with accurate spatial control. In the attempt to create  NFES has suffered a number of variations

Lorem ipsum dolor sit amet

One-dimensional (1-D) nanostructures have attracted enormous research interest due to their unique physicochemical properties and wide application potential. These 1-D nanofibers are being increasingly applied to biomedical fields owing to their high surface area-to-volume ratio, high porosity, and the ease of tuning their structures, functionalities, and properties. Many biomedical nanofiber reviews have focused on tissue engineering and drug delivery applications but have very rarely discussed their use as wound dressings. However, nanofibers have enormous potential as wound dressings and other clinical applications that could have wide impacts on the treatment of wounds. Herein, the authors review the main fabrication methods of nanofibers as well as requirements, strategies, and recent applications of nanofibers, and provide perspectives of the challenges and opportunities that face multifunctional nanofibers for active therapeutic applications.

Near field electrospinning is one of the leading techniques in accurate placement of nanofibers. This technique has evolved from using AFM tips to supply a limited volume of solution for electrospinning to nozzle-based system where a continuous stream of solution can be extruded.

The precision and accuracy of the fiber deposition has also vastly improved from simple formation of oriented fibers on a collector to precise deposition of the fiber at a specific point. Despite the progress, several intrinsic limitation or characteristic of near-field electrospinning still needs to be noted when employing this technique.
\end{abstract}
\begin{keyword} 
      polymer\sep solvent\sep near-field electrospinning\sep NFES\sep fibers\sep spatial control
\end{keyword}

@@

\section{Introduction}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

@@

  \textbf{Solution Concentration:} SU-8/PEO/TBF blend with 0.75$wt\% $ PEO, 1$wt\% $ TBF; the blend is diluted with 30$vol\% $ DMF \mbox{}\protect\newline \textbf{Nozzle:} needle inner diameter of 533$\mu m $ and outer diameter of 710$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:}\textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:}\textit{Not determined} \mbox{}\protect\newline \textbf{Substrate composition:} Brass disk with a diameter of 38$mm $ \mbox{}\protect\newline \textbf{Applied voltage:} 980$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:}\textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &

>>>>

\begin{abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
\end{abstract}
\begin{keyword} 
      polymer\sep solvent\sep near-field electrospinning\sep NFES\sep fibers\sep spatial control
\end{keyword}

@@

\section{Introduction}
Diverse polymer patterning techniques have been developed for the fabrication of nano-fibers, such as arc discharge [31], chemical vapor deposition, laser ablation [21], and vapor growth [18]. Nonetheless, those processes are expensive due to either the low product yield or the expensive equipment required. The electrospinning method (invented by Formhals Anton in 1934)can produce fibers with a range of diameters between 10 nm and 10 mm [12,2] from a polymer solution under the influence of an electrostatic force. The applied electric field and solution conductivity and viscosity is an important parameter the affects the fiber diameter during the spinning along with other parameters such as jet length, solution viscosity surrounding gas, flow rate and the collector geometry [1, 14, 4, 26].

Even though electrospinning is an old invention [2], it is currently a trending topic among researchers [11, 22, 23]. One of the reasons electrospinning is to be studied is its potential to fabricate polymer nano-fibers from a variety of polymers. The technique allows the production of thin continuous fibers with ease, with diameters down to 3 nm in some cases, which is something difficult to achieve by other techniques. Furthermore, the basic setup can be modified with ease to fabricate different fibers with diversified functionalities with different materials. The produced fibers can be aligned or unaligned. Besides, the electrospinning equipment is inexpensive and of small size, compared to the equipment of standard spinning techniques. On the other hand, the understanding of the electrospinning process has improved in the last years [15]. As Reneker and Yarin state: "Electrospinning has rapidly changed fiber making from a capital intensive, large scale process to a low cost, broadly applicable method that manufactures fibers on a laboratory bench, to serve diverse needs ranging from materials science and technology to life sciences and clinical medicine.`` [22]

The main components of the electrospinning technique are the fluid control unit (e.g. syringe pump) and a DC power supply. The process also requires a target electrode or combination of electrodes on which the fibers can be collected. Figure 6.2 describes a typical electrospinning set-up. [15] Two sub-techniques can be derived from electrospinning depending on the distance between the dispensing electrode and the collector. The process in which the electrospun jet can be controlled near the tip is called NFES or near-field electrospinning. [7] Moreover, if the distance between the collector and the dispensing needle is greater, the configuration is known as FFES or far-field electrospinning. [19] The difference between NFES and mechano-electrospinning is the presence of a mechanical collector that allows higher precision when patterning. Figure 6.3 shows a typical near field mechano-electrospinning apparatus.

@@

  \textbf{Solution Concentration:} SU-8/PEO/TBF blend with 0.75$wt\% $ PEO, 1$wt\% $ TBF; the blend is diluted with 30$vol\% $ DMF \mbox{}\protect\newline $\mu m $$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:}\textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:}\textit{Not determined} \mbox{}\protect\newline \textbf{Substrate composition:} Brass disk with a diameter of 38$mm $ \mbox{}\protect\newline \textbf{Applied voltage:} 980$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:}\textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
